---
title: "exploration"
author: "Amber Thomas"
date: "3/14/2019"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro

This is an exploration of songs that contain names (from a Kaggle corpus of 57k songs searching for over 3k names that have been used more than 5k times between the 1950's and now).

## Packages

```{r messages = FALSE}
library(tidyverse)
library(here)
library(data.table)
library(gender)
library(Rspotify)
library(sentimentr)
library(magrittr)
library(glue)
```
## Preparing data

Let's start by just loading the data.
```{r}
#nameData <- fread(here::here("processed_data", "songNames.csv"), data.table =FALSE)
nameData <- fread(here::here("raw_data", "topSongNames.csv"), data.table =FALSE)

```

## Exploration

How many songs (out of 40k) had a name in it?

```{r}
count <- nameData %>% distinct(artist, song) %>% summarise(count = n())
```
Ok, so there's `r count` (`r (count/40000) * 100`%) songs with names. 


Let's limit to just the ones that are "proper nouns" and filter out any where the sentence is just the name in parentheses or brackets.

```{r}
proper <- allSongNames %>% 
  filter(upos == "PROPN") %>% 
  mutate(sentence = gsub("(\\(|\\[).*(\\)|\\])", "", sentence)) %>% 
  filter(sentence != "")
```
 
### Most Common Names 
Ok, out of those, which are the most common?

```{r}
common <- proper %>% 
  count(name, sort = TRUE)

common
```

### By Artist

Which artists use the most names?

```{r}
byArtist <- proper %>% 
  distinct(artist, song) %>% 
  count(artist, sort = TRUE)

byArtist
```

Woah, some of these artists have a lot of songs with names! Let's look at `Drake`.

```{r}
drake <- proper %>% 
  filter(artist == "Drake") %>%  
  distinct(song, .keep_all = TRUE) %>% 
  count(name, sort = TRUE)

drake
```

Ok, so some of these are most likely references to places (i.e., `Brooklyn`, `America`) or things (`Bentley`). Let's look at `John`.

```{r}
johnFab <- proper %>% 
  filter(artist == "Fabolous" & name == "John")

johnFab$sentence
```

Well, that seems to check out. Let's spot check someone from a different genre: `Jimmy Buffett`

```{r}
buff <- proper %>% 
  filter(artist == "Jimmy Buffett") %>%  
  distinct(song, .keep_all = TRUE) %>% 
  count(name, sort = TRUE)

buff
```

He says his own name a lot. Let's make sure that looks right:

```{r}
jimmyBuff <- proper %>% 
  filter(artist == "Jimmy Buffett" & name == "Jimmy")

jimmyBuff$sentence
```

Ah, we've got a minor data issue where his name has been inserted into the lyrics to indicate that he is speaking. I'll have to think about how to remove this.

Let's check one more: `Cher`.

```{r}
cher <- proper %>% 
  filter(artist == "Cher") %>%  
  distinct(song, .keep_all = TRUE) %>% 
  count(name, sort = TRUE)

cher
```

How many of these names are the artists' own name (either purposely in the data or a data-error?)

```{r}
own <- proper %>% 
  mutate(own = str_detect(artist, regex(glue("\\b{name}([:space:]|\\n)"))))

ownName <- own %>% 
  filter(own == TRUE)

notOwn <- own %>% 
  filter(own == FALSE)
```

Alright, so that's not too bad, only `r nrow(ownName)` or (`r (nrow(ownName)/nrow(proper)) * 100`%) of songs conceivably have this error. 

### Song with most names

Which songs say the same name the most times?

```{r}
most <- proper %>% 
  group_by(artist, song, name) %>%  
  summarise(count = n()) %>% 
  ungroup() %>% 
  arrange(desc(count))

head(most, n = 50)
```

And which songs have the most different names?

```{r}
different <- proper %>% 
  group_by(artist, song) %>% 
  distinct(name) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))

head(different, n = 50)
```

### Gendered Difference in Names

Using the `genderizeR` package, can we look at the top `male` vs. `female` (predicted) names? 

```{r}
findGender <- function(name){
  years <- c(1963, 2012)
  
  gender(name, years)
}

genderedNames <- map_dfr(common$name, findGender)

cleanGenderedNames <- genderedNames %>% 
  mutate(gen = ifelse(proportion_male >= 0.6, "male",
                      ifelse(proportion_female >= 0.6, "female", "unknown")))

countGendered <- proper %>% 
  count(name, sort = TRUE) %>% 
  left_join(cleanGenderedNames) %>% 
  select(c(name, n, gen)) %>% 
  group_by(gen) %>% 
  arrange(desc(n)) %>% 
  mutate(rank = row_number()) %>% 
  filter(rank <= 20)

countGendered
```


### Adding Sentiment Data

Anything interesting about the sentiment of a song with different names? 

```{r}
distinctSongs <- proper %>% 
  distinct(artist, song, .keep_all = TRUE) 

sentiment <- distinctSongs %>% 
  dplyr::mutate(dialogue_split = get_sentences(sentence)) %$%
  sentiment_by(dialogue_split, list(artist, song))

sentimentByName <- proper %>% 
  left_join(sentiment, by = c("artist", "song")) 

sentimentGroup <- sentimentByName %>% 
  group_by(name) %>% 
  summarise(count = n(),
            avg = mean(ave_sentiment),
            stdev = sd(ave_sentiment)) %>% 
  arrange(desc(count)) %>% 
  filter(count >= 5)

namesToCheck <- head(sentimentGroup, n = 20) %$%
  name

limitedNames <- sentimentByName %>% 
  filter(name %in% namesToCheck)
  

ggplot(limitedNames, aes(x = factor(name), y = ave_sentiment)) +
  geom_boxplot(alpha = 0.80) +
  geom_point(aes(fill = "name"), size = 2, shape = 21, position = position_jitterdodge())  +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


How about the songs with the highest sentiment? 

```{r}
highestNames <- sentimentByName %>% 
  distinct(song, .keep_all = TRUE) %>% 
  group_by(name) %>% 
  summarise(count = n(),
            avg = mean(ave_sentiment),
            stdev = sd(ave_sentiment)) %>% 
  arrange(desc(avg)) %>% 
  filter(count >= 10)

namesToCheck <- head(highestNames, n = 20) %$%
  name

limitedNames <- sentimentByName %>% 
  filter(name %in% namesToCheck)
  

ggplot(limitedNames, aes(x = factor(name), y = ave_sentiment)) +
  geom_boxplot(alpha = 0.80) +
  geom_point(aes(fill = "name"), size = 2, shape = 21, position = position_jitterdodge()) + theme(legend.position="none") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


Or the lowest sentiment
```{r}
lowestNames <- sentimentByName %>% 
  distinct(song, .keep_all = TRUE) %>% 
  group_by(name) %>% 
  summarise(count = n(),
            avg = mean(ave_sentiment),
            stdev = sd(ave_sentiment)) %>% 
  arrange((avg)) %>% 
  filter(count >= 10)

namesToCheck <- head(lowestNames, n = 20) %$%
  name

limitedNames <- sentimentByName %>% 
  filter(name %in% namesToCheck)
  

ggplot(limitedNames, aes(x = factor(name), y = ave_sentiment)) +
  geom_boxplot(alpha = 0.80) +
  geom_point(aes(fill = "name"), size = 2, shape = 21, position = position_jitterdodge()) + theme(legend.position="none") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


Or the name with the lowest variation in sentiment? 

```{r}
lowestVar <- sentimentByName %>% 
  distinct(song, .keep_all = TRUE) %>% 
  group_by(name) %>% 
  summarise(count = n(),
            avg = mean(ave_sentiment),
            stdev = sd(ave_sentiment)) %>% 
  arrange((stdev)) %>% 
  filter(count >= 10)

namesToCheck <- head(lowestVar, n = 20) %$%
  name

limitedNames <- sentimentByName %>% 
  filter(name %in% namesToCheck)
  

ggplot(limitedNames, aes(x = factor(name), y = ave_sentiment)) +
  geom_boxplot(alpha = 0.80) +
  geom_point(aes(fill = "name"), size = 2, shape = 21, position = position_jitterdodge()) + theme(legend.position="none") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


```{r}
alyssa <- proper %>% 
  filter(artist == "Sir Mix") 

alyssa
```


## Other Possibilities

* Generate playlist of songs for each name
* Look at change over time
* Look at names by genre

```{r}
songs <- proper %>% 
  count(artist, song)
```


