---
title: "Full Exploration"
author: "Amber Thomas"
date: "4/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro

Ok, so now we have data on all the names found in x top songs from Billboard's Hot 100!

We'll start with loading some necessary packages. 

```{r load_packages}
library(tidyverse)
library(here)
library(gender)
library(sentimentr)
library(googledrive)
```

and the data

```{r eval = FALSE}
#allNameSongs <- read.csv(here::here("processed_data", "allNamesInSongs.csv"), header = TRUE, stringsAsFactors = FALSE)
```

and the manually cleaned data 

```{r}
sheetID <- googledrive::as_id("https://docs.google.com/spreadsheets/d/1TW1skGoCvdOyIdjD-2yjiQ6YWAA6EdJTk9g03FeHYtM/edit#gid=772914444")

googledrive::drive_download(sheetID, path = here("raw_data", "allSongsManualClean.csv"), overwrite = TRUE)

allNameSongs <- read.csv(here::here("raw_data", "allSongsManualClean.csv"), stringsAsFactors = FALSE, header = TRUE, na.strings = c("", " ", "none"))
```

and the few that were missing/noticeably mis-tagged in our cleaned dataset

```{r}
sheetID <- googledrive::as_id("https://docs.google.com/spreadsheets/d/1r5MeitTTbY5tkNP21yOrBrdWolmaPmivUbN5pC2pl94/edit#gid=214384950")

googledrive::drive_download(sheetID, path = here("raw_data", "chosenSongsManualClean.csv"), overwrite = TRUE)

artist <- c("Justin Bieber", "Elton John", "The Oak Ridge Boys", "Tony Bennett", "Ricky Martin", "The Four Seasons")
song <- c("Baby", "Bennie and the Jets", "Elvira", "When Joanna Loved Me", "Maria", "Sherry")
year <- c(2010, 1974, 1981, 1964, 1996, 1962)
highestRank <- c(5, 1, 5, 94, 88, 1)

crosswalk <- tibble(artist = artist,
                    song = song,
                    year = year,
                    highestRank = highestRank)

manualNameSongs <- read.csv(here::here("raw_data", "chosenSongsManualClean.csv"), stringsAsFactors = FALSE, header = TRUE, na.strings = c("", " ", "none")) %>% 
  left_join(crosswalk)
```
Now to remove those songs from the first dataset:

```{r}
songsToRemove <- c("Baby", "Bennie and the Jets", "Elvira")

`%notIn%` <- purrr::negate(`%in%`)

allMinusChosen <- allNameSongs %>% 
  filter(song %notIn% songsToRemove) %>% 
  select(-earliest)
```

and add the correct versions in: 

```{r}
allNames <- rbind(allMinusChosen, manualNameSongs)
```




## Processing Data

Most of the processing has already been done, but we can limit our results to just names that were identified as Proper Nouns either manually or programmatically. We also need to remove last names, and substitute double names (like "Barbara Ann" or "Mary Sue") with the single names tagged by the system.  

```{r defining_proper}
proper <- allNames %>% 
  mutate(manualPOS = ifelse(is.na(posCorrection), upos, posCorrection),
         manualName = ifelse(is.na(compound), name, compound)) %>% 
  filter(manualPOS == "PROPN",
         is.na(last)) %>% 
  select(-c(name)) %>% 
  rename(name = manualName,
         nonPerson = NaP) %>% 
  select(-c("upos", "xpos", "dep_rel", "posCorrection", "last", "compound", "manualPOS"))
```

Let's also split out our data, to just names, and names that could include other things (brands, drugs, cities, etc.)

```{r defining_justnames}
justNames <- proper %>% 
  filter(is.na(nonPerson))
```

## Exploration

### Common Names

Alright, let's start simple. What are the most common names used overall? 

```{r defining_common}
common <- justNames %>% 
  count(name, sort = TRUE)

common
```

Out of the `nrow(common)` names used across all of our songs. The most common names are `common[1,1]`, `common[1,2]`, and `common[1,3]`. But that is a total of mentions of each name. Let's see which ones are the most common across each song (that is, counting each song that mentions a name only once).

```{r}
commonBySong <- justNames %>% 
  group_by(artist, song) %>% 
  distinct(name, .keep_all = TRUE) %>% 
  ungroup() %>% 
  count(name, sort = TRUE)

commonBySong
```

Pretty similar. The top names are now `commonBySong[1,1]`, `commonBySong[2,1]`, and `commonBySong[3,1]`.


### By Artist

Do certain artists use names in more songs than others? 

```{r}
artist <- justNames %>% 
  group_by(artist) %>% 
  distinct(song, .keep_all = TRUE) %>% 
  ungroup() %>% 
  count(artist, sort = TRUE) %>% 
  mutate(person = TRUE)

artist

artistNP <- proper %>% 
  group_by(artist) %>% 
  distinct(song, .keep_all = TRUE) %>% 
  ungroup() %>% 
  count(artist, sort = TRUE) %>% 
  mutate(person = FALSE)

allArtist <- rbind(head(artist, n = 10), head(artistNP, n = 10))

#write.csv(allArtist, "../src/assets/data/artist.csv", row.names = FALSE)
```

Well, with the exception of `Glee Cast` (who just sing lots of popular songs), most of these artists are rappers or Hip Hop artists. Let's see if the most popular are consistently singing about the same names. 

We'll start with Drake, who has names in 49 of his top songs!

```{r}
drake <- justNames %>% 
  filter(artist == "Drake") %>% 
  distinct(song, .keep_all = TRUE) %>% 
  count(name, sort = TRUE)

drake
```

Wow, with `nrow(drake)` different names in his repertoire, Drake is rarely singing about the same person in multiple songs.

Let's check with our #2 artist, Eminem. 

```{r}
eminem <- justNames %>% 
  filter(artist == "Eminem") %>% 
  distinct(song, .keep_all = TRUE) %>% 
  count(name, sort = TRUE)

eminem
```

Although Eminem also doesn't include the same name too repetitively, it's unsurprising that he uses the name "Hailie" in 3 separate songs and "Hailie Jade" in another. Hailie is his daughter's name, afterall. 

### Repeat Names

Some songs (like Jolene or Barbara Anne) use the same name over and over again. Which songs use the same name repeatedly?

```{r}
repeats <- justNames %>% 
  group_by(artist, song) %>% 
  count(name) %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  filter(n > 15)

repeats
```
Let's find the single song with the most mentions of every name.

```{r repeat_names}
repeatInd <- proper %>% 
  # add a column to denote whether or not the name is likely reffering to a person
  mutate(person = ifelse(is.na(nonPerson), TRUE, FALSE)) %>% 
  group_by(artist, song, person) %>% 
  # count the number of times a name was used inside a song
  count(name, sort = TRUE) %>% 
  # Keep only the top name per song
  mutate(row = row_number()) %>% 
  filter(row == 1) %>%  
  select(-row) %>% 
  ungroup() 
```
```{r}
write.csv(repeatInd, "../src/assets/data/repeats.csv", row.names = FALSE)
  
```

### Different Names

On the flip side, which songs use the most unique names? 

```{r}
uniqueNames <- justNames %>% 
  group_by(artist, song) %>% 
  distinct(name, .keep_all = TRUE) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count)) %>% 
  filter(artist != "R. Kelly")

uniqueNames
```

```{r}
unNameOut <- proper %>% 
  mutate(person = ifelse(is.na(NaP), TRUE, FALSE)) %>% 
  group_by(artist, song) %>% 
  distinct(name, .keep_all = TRUE) %>% 
  select(c("artist", "name", "song", "person"))  %>% 
  filter(artist != "R. Kelly")

write.csv(unNameOut, "../src/assets/data/unique.csv", row.names = FALSE)
```

```{r output_popular}
# Export just the distinct names mentioned by artists per song
byNameOut <-  proper %>% 
  # add column which indicates if a name represents a person or something else
  mutate(person = ifelse(is.na(nonPerson), TRUE, FALSE)) %>% 
  # find distinct names mentioned by an artist in each song
  group_by(artist, song) %>% 
  distinct(name, .keep_all = TRUE) %>% 
  # remove any excess white space around the names
  mutate(name = trimws(name)) %>% 
  # filter out this R.Kelly song
  filter(song != "She's Got That Vibe") %>% 
  # keep only
  select(c("artist", "name", "song", "person", "sentence", "year", "highestRank")) %>% 
  ungroup()
```

```{r}
write.csv(byNameOut, "../src/assets/data/popular.csv", row.names = FALSE)
```



```{r name_per_artist}
# Find the number of songs that each artist uses a name in
unNameArtist <- proper %>% 
  # create column indicating if name refers to a person or not
  mutate(person = ifelse(is.na(nonPerson), TRUE, FALSE)) %>% 
  # keep all names used distinctly by the artist in each song
  group_by(artist, song) %>% 
  distinct(name, .keep_all = TRUE) %>% 
  # count the number of songs that contain each name 
  group_by(artist, person, name) %>% 
  summarise(n = n()) 
```

```{r songs_per_artist}
# Find the number of songs each artist has that contain names (regardless of usage)
artistLookupAll <- proper %>% 
  group_by(artist) %>% 
  # Find just unique songs by that artist
  distinct(song) %>% 
  # Count how many there are
  summarise(count = n()) %>% 
  # Add a column indicating that the name could refer to people & non-people
  mutate(person = FALSE)

# Find the number of songs each artist has that contain names (that represent people only)
artistLookup<- proper %>% 
  # Filter names not used to represent a person
  filter(is.na(nonPerson)) %>% 
  group_by(artist) %>% 
  # Find just unique songs by that artist
  distinct(song) %>% 
  # Count how many there are
  summarise(count = n()) %>% 
  # add a column indicating that the names are only people
  mutate(person = TRUE)

# Combine the above data frames by row
allLookup <- rbind(artistLookup, artistLookupAll)

# Bind with our count of name mentions per artist
unNameArtistLookup <- unNameArtist %>% 
  left_join(allLookup) %>% 
  # Change the column names
  rename(names = n, songs = count)
```

```{r}
write.csv(unNameArtistLookup, "../src/assets/data/artist.csv", row.names = FALSE)
```




### First Letter

Back in 2014, Slate published an [article](https://slate.com/culture/2014/07/most-common-names-in-songs-why-is-pop-music-obsessed-with-songs-about-johnny-jenny-and-jane.html) about how pop songs that have names in the _titles_ most often contain names that start with J. Do we see the same trend with names in the lyrics? 

```{r}
firstLetter <- justNames %>% 
  mutate(first = str_sub(name, 1, 1)) %>% 
  distinct(name, .keep_all = TRUE) %>% 
  ungroup() %>% 
  count(first, sort = TRUE)
```

```{r}
ggplot(firstLetter, aes(x = first, y = n)) + geom_bar(stat = "identity")
```

How does this compare to the Social Security name data that we have? 

```{r}
onlyNames <- read.csv(here::here("processed_data", "onlyNames.csv"), header = TRUE, stringsAsFactors = FALSE) 

onlyNamesClean <- onlyNames %>% rename(name = Name)

onlyNameLetter <- onlyNames %>% 
  mutate(first = str_sub(Name, 1, 1)) %>% 
  count(first, sort = TRUE) %>% 
  mutate(percent = (n / nrow(onlyNames)) * 100,
         group = "SS")

firstLetterPercent <- justNames %>% 
  mutate(first = str_sub(name, 1, 1)) %>% 
  distinct(name, .keep_all = TRUE) %>% 
  ungroup() %>% 
  count(first, sort = TRUE) %>% 
  mutate(percent = (n / nrow(common)) * 100,
         group = "song")

firstLettersAll <- rbind(onlyNameLetter, firstLetterPercent)
```

```{r}
ggplot(firstLettersAll, aes(x = first, y = percent, group = group, fill = group)) + geom_bar(stat = "identity", position = "dodge")
```
Huh, names starting with B, C, P, R, and S are quite a bit more popular in songs than in the actual country. A names and D names are slightly less common and K and L names are wayyy less common in songs than in the country.


```{r names_function}
findLetters <- function(data, position, condition){
  data %>% 
    # find either first or last letter, depending on position argument
    mutate(letter = case_when(
      position == "first" ~ str_sub(name, 1, 1),
      position == "last" ~ str_sub(name, -1 ,-1)
    )) %>% 
    # Create new column with position information
    mutate(position = position) %>% 
    # Find all of the distinct names
    distinct(name, .keep_all = TRUE) %>% 
    ungroup() %>% 
    # count all the names that start or end with each letter
    count(letter, sort = TRUE) %>% 
    # calculate percent of names from the condition that start or end
    # the same way
    mutate(percent = case_when(
      condition == "song" ~ (n / nrow(common)) * 100,
      condition == "society" ~ (n / nrow(onlyNames) * 100)
    ),
    group = condition
    )
}
```


```{r compare_conditions}
compareConditions <- function(songCondition, societyCondition, person, position){
  # combine song and society conditions
  all <- rbind(songCondition, societyCondition) %>% 
    # remove the count column
    select(-n) %>% 
    # convert our long data to wide
    spread(group, percent) %>% 
    # calculate percentage difference between conditions
    mutate(dif = song - society,
           position = position, 
           person = person) %>% 
    # Remove unneccessary columns
    select(-c(society, song))
}

```

```{r running_names_function}
# Finding counts & percentages for first letters
songFirst <- findLetters(justNames, "first", "song")
societyFirst <- findLetters(onlyNamesClean, "first", "society")

# Finding counts & percentages for last letters
songLast <- findLetters(justNames, "last", "song")
societyLast <- findLetters(onlyNamesClean, "last", "society")

# Finding counts of names in songs for non-people
songFirstNP <- findLetters(proper, "first", "song")
songLastNP <- findLetters(proper, "last", "song") 


# Combine the song starting letters with the society starting letters
allFirst <- compareConditions(songFirst, societyFirst, TRUE, "first")
allLast <- compareConditions(songLast, societyLast, TRUE, "last")
allFirstNP <- compareConditions(songFirstNP, societyFirst, FALSE, "first")
allLastNP <- compareConditions(songLastNP, societyLast, FALSE, "last")

# Combine all results
allLetters <- rbind(allFirst, allLast, allFirstNP, allLastNP) %>% 
  # capitalize all letters
  mutate(letter = toupper(letter))
  
```


```{r}
firstLetterPercent <- justNames %>% 
  mutate(first = str_sub(name, 1, 1)) %>% 
  distinct(name, .keep_all = TRUE) %>% 
  ungroup() %>% 
  count(first, sort = TRUE) %>% 
  mutate(percent = (n / nrow(common)) * 100,
         group = "song")

firstLettersAll <- rbind(onlyNameLetter, firstLetterPercent)
firstLetterDif <- firstLettersAll %>% 
  select(-n) %>% 
  spread(group, percent) %>% 
  mutate(dif = song - SS) %>% 
  select(c("first", "dif")) %>% 
  mutate(person = TRUE,  
         letter = first,
         pos = "first") %>% 
  select(-first)

ggplot(firstLetterDif, aes(x = first, y = dif)) + geom_bar(stat = "identity")
```

```{r}
firstLetterPercentNP <- proper %>% 
  mutate(first = str_sub(name, 1, 1)) %>% 
  distinct(name, .keep_all = TRUE) %>% 
  ungroup() %>% 
  count(first, sort = TRUE) %>% 
  mutate(percent = (n / nrow(common)) * 100,
         group = "song")

firstLettersAllNP <- rbind(onlyNameLetter, firstLetterPercentNP)
firstLetterDifNP <- firstLettersAllNP %>% 
  select(-n) %>% 
  spread(group, percent) %>% 
  mutate(dif = song - SS) %>% 
  select(c("first", "dif")) %>% 
  mutate(person = FALSE,  
         letter = first,
         pos = "first") %>% 
  select(-first)
```


What about letters that end a name? 

```{r}
lastLetter <- justNames %>% 
  mutate(last = str_sub(name, -1, -1)) %>% 
  distinct(name, .keep_all = TRUE) %>% 
  ungroup() %>% 
  count(last, sort = TRUE)

lastLetter
```

Names that end in E are reigning supreme here. 


```{r}
onlyNameLetterLast <- onlyNames %>% 
  mutate(last = str_sub(Name, -1, -1)) %>% 
  count(last, sort = TRUE) %>% 
  mutate(percent = (n / nrow(onlyNames)) * 100,
         group = "SS")

lastLetterPercent <- justNames %>% 
  mutate(last = str_sub(name, -1, -1)) %>% 
  distinct(name, .keep_all = TRUE) %>% 
  ungroup() %>% 
  count(last, sort = TRUE) %>% 
  mutate(percent = (n / nrow(common)) * 100,
         group = "song")

lastLettersAll <- rbind(onlyNameLetterLast, lastLetterPercent)

lastLetterDif <- lastLettersAll %>% 
  select(-n) %>% 
  spread(group, percent) %>% 
  mutate(dif = song - SS) %>% 
  select(c("last", "dif")) %>% 
  mutate(person = TRUE,  
         letter = last,
         pos = "last") %>% 
  select(-last)

ggplot(lastLetterDif, aes(x = first, y = dif)) + geom_bar(stat = "identity")

```


```{r}
onlyNameLetterLast <- onlyNames %>% 
  mutate(last = str_sub(Name, -1, -1)) %>% 
  count(last, sort = TRUE) %>% 
  mutate(percent = (n / nrow(onlyNames)) * 100,
         group = "SS")

lastLetterPercentNP <- proper %>% 
  mutate(last = str_sub(name, -1, -1)) %>% 
  distinct(name, .keep_all = TRUE) %>% 
  ungroup() %>% 
  count(last, sort = TRUE) %>% 
  mutate(percent = (n / nrow(common)) * 100,
         group = "song")

lastLettersAllNP <- rbind(onlyNameLetterLast, lastLetterPercentNP)

lastLetterDifNP <- lastLettersAllNP %>% 
  select(-n) %>% 
  spread(group, percent) %>% 
  mutate(dif = song - SS) %>% 
  select(c("last", "dif")) %>% 
  mutate(person = FALSE,
         letter = last,
         pos = "last") %>% 
  select(-last)

allLetters <- rbind(firstLetterDif, firstLetterDifNP, lastLetterDif, lastLetterDifNP) %>% 
  mutate(letter = toupper(letter))

write.csv(allLetters, "../src/assets/data/letters.csv", row.names = FALSE)

```


What are the most popular names that end in Y?

```{r}
endY <- justNames %>% 
  mutate(last = str_sub(name, -1, -1)) %>%
  filter(last == "y") %>% 
  count(name, sort = TRUE)
```

```{r}
endA <- justNames %>% 
  mutate(last = str_sub(name, -1, -1)) %>%
  filter(last == "a") %>% 
  count(name, sort = TRUE)
```


### Gendered Names

Anecdotally, it looks like there are more male names mentioned than female names. Let's check that out. 

Using the `gender` package, can we look at the top `male` vs. `female` (predicted) names? 

```{r}
findGender <- function(name){
  years <- c(1963, 2012)
  
  gender::gender(name, years)
}

genderedNames <- map_dfr(common$name, findGender)

cleanGenderedNames <- genderedNames %>% 
  mutate(gen = ifelse(proportion_male >= 0.6, "male",
                      ifelse(proportion_female >= 0.6, "female", "unknown")))

countGendered <- justNames %>% 
  count(name, sort = TRUE) %>% 
  left_join(cleanGenderedNames) %>% 
  select(c(name, n, gen)) %>% 
  group_by(gen) %>% 
  arrange(desc(n)) %>% 
  mutate(rank = row_number()) %>% 
  filter(rank <= 20)

countGendered
```

How many songs contain male names vs. female names? 

```{r}
maleFemaleSongs <- justNames %>% 
  left_join(cleanGenderedNames) %>% 
  group_by(artist, song) %>% 
  distinct(name, .keep_all = TRUE) %>% 
  ungroup() %>% 
  count(gen, sort = TRUE)

maleFemaleSongs
```

There are almost twice as many male names (`maleFemaleSongs[1,2]`) mentioned in songs as female names (`maleFemaleSongs[2,2]`)!

### By Decade

Let's take a look at the top names by decade

```{r by_decade}
# Find the most popular ten names per decade 
# (only names that refer to people)
byDecade <- justNames %>% 
  # make sure year is read as a number, not a character
  mutate(year = as.integer(year)) %>% 
  # calculate which decade the year fell into
  mutate(decade = year - year %% 10) %>% 
  # Find unique names in each decade, artist, song, combination
  group_by(decade, artist, song) %>% 
  distinct(name, .keep_all = TRUE) %>% 
  ungroup() %>% 
  # Count the number of songs include a name in each decade
  group_by(decade) %>% 
  count(name, sort = TRUE) %>% 
  # rank each name based on its count
  mutate(rank = row_number()) %>% 
  # Keep only the top 10
  filter(rank <= 10) %>% 
  filter(!is.na(decade)) %>% 
  # Remove any from 1950's since the Billboard Charts started in 1958
  filter(decade != "1950") %>% 
  mutate(person = TRUE)

# Find the most popular ten names per decade
# names referring to anything 
byDecadeAll <- proper %>% 
  mutate(year = as.integer(year)) %>% 
  mutate(decade = year - year %% 10) %>% 
  group_by(decade, artist, song) %>% 
  distinct(name, .keep_all = TRUE) %>% 
  ungroup() %>% 
  group_by(decade) %>% 
  count(name, sort = TRUE) %>% 
  mutate(rank = row_number()) %>% 
  filter(rank <= 10) %>% 
  filter(!is.na(decade)) %>% 
  filter(decade != "1950") %>% 
  mutate(person = FALSE)

# Combine the above data frames
decades <- rbind(byDecade, byDecadeAll)
```

```{r}

write.csv(decades, "../src/assets/data/decade.csv", row.names = FALSE)

```

```{r}

my_theme <- function() {

  # Colors
  color.background = "white"
  color.text = "#22211d"

  # Begin construction of chart
  theme_bw(base_size=15) +

    # Format background colors
    theme(panel.background = element_rect(fill=color.background, color=color.background)) +
    theme(plot.background  = element_rect(fill=color.background, color=color.background)) +
    theme(panel.border     = element_rect(color=color.background)) +
    theme(strip.background = element_rect(fill=color.background, color=color.background)) +

    # Format the grid
    theme(panel.grid.major.y = element_blank()) +
    theme(panel.grid.minor.y = element_blank()) +
    theme(axis.ticks       = element_blank()) +

    # Format the legend
    theme(legend.position = "none") +

    # Format title and axis labels
    theme(plot.title       = element_text(color=color.text, size=20, face = "bold")) +
    theme(axis.title.x     = element_text(size=14, color="black", face = "bold")) +
    theme(axis.title.y     = element_text(size=14, color="black", face = "bold", vjust=1.25)) +
    theme(axis.text.x      = element_text(size=10, vjust=0.5, hjust=0.5, color = color.text)) +
    theme(axis.text.y      = element_text(size=10, color = color.text)) +
    theme(strip.text       = element_text(face = "bold")) +

    # Plot margins
    theme(plot.margin = unit(c(0.35, 0.2, 0.3, 0.35), "cm"))
}

show.top.n <- 10

ggplot(data = byDecade, aes(x = decade, y = rank, group = name)) +
  geom_line(aes(color = name, alpha = 1), size = 2) +
  geom_point(aes(color = name, alpha = 1), size = 4) +
  geom_point(color = "#FFFFFF", size = 1) +
  scale_y_reverse(breaks = 1:show.top.n) +
  #scale_x_continuous(breaks = 1950:2010, minor_breaks = 1950:2010, expand = c(.05, .05)) +
  geom_text(data = byDecade %>% filter(decade == 1950),
            aes(label = name, x = 1950) , hjust = .15, fontface = "bold", color = "#888888", size = 3) +
  geom_text(data = byDecade %>% filter(decade == 2010),
            aes(label = name, x = 2010) , hjust = 0.85, fontface = "bold", color = "#888888", size = 3) +
  coord_cartesian(ylim = c(1,show.top.n)) + 
  theme(legend.position = "none") +
  labs(x = "Decade",
       y = "Rank") +
  my_theme() 

# ggplot(byDecade, aes(x = decade, y = rank, group = name)) +
#   geom_line(aes(color = name, alpha = 1), size = 2) +
#   geom_point(aes(color = name, alpha = 1), size = 4) +
#   scale_y_reverse(breaks = 1:nrow(byDecade))
```


### Manual Corrections 
Send to Google Docs for manual corrections. New columns: 

* posCorrect: was the part of speech mislabeled? What should the label be? 
* NaP: is this name referencing something that's "Not a Person"? 
* last: is this referring to a last name? 
* compound: What is the compound name (like "Barbara Ann")? 

Let's upload `allNameSongs` to google drive. 

```{r}
googledrive::drive_upload(media = here::here("processed_data", "allNamesInSongs.csv"), 
             path = "names in songs/", 
             name = "namesInSongs", 
             type = "spreadsheet")
```


